draft_final_assignment

### 2022-11-30 draft_final_assingment.Rmd
Nov30draft

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
```

@@

## Creating party variable
```{r }
#if two thirds of the sponsors are democrats, we consider the bill democrat-dominated
#same for republicans
#if there is no clear majority, they are "Both"
df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```

@@

@@

ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw()
```

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

@@

## Creating party variable
```{r }
#if two thirds of the sponsors are democrats, we consider the bill democrat-dominated
#same for republicans
#if there is no clear majority, they are "Both"

df$party <- ifelse(df$cosponsor_D_perc > 0.66, "Democrat", ifelse(df$cosponsor_R_perc > 0.66, "Republican", "Both"))
```

@@

##Dimensionality plotting

@@

p <- ggplot(df, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict) +
  theme_bw()

p
ggplotly(p)
```

```{r }
df1 <- df %>%
  mutate(party_full = ifelse(cosponsor_D_perc == 1.0, "Dem",
                             ifelse(cosponsor_R_perc == 1.0, "Rep", NA))) %>%
  drop_na(party_full)

corp3 <- corpus(df1$summary)

dfmat3 <- corp3 %>%
  tokens(remove_punct = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  dfm() %>%
  dfm_trim(min_termfreq = 5)

embeddings2 <- umap(as.matrix(dfmat3))

df1$x <- embeddings2[,1]
df1$y <- embeddings2[,2]

colordict2 <- c( "Democrat"="blue","Republican"="red")

j <- ggplot(df1, aes(x, y, fill=party)) + 
  geom_point(color="grey", shape=21, size=0.5) + 
  scale_fill_manual(values=colordict2) +
  theme_bw()

j
ggplotly(j)
```
